---
title: "Beer Case Study"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r GatherData}
require(plyr)
require(dplyr)
require(tidyr)
require(ggplot2)

beers <- read.csv("Dataset/Beers.csv",stringsAsFactor=FALSE)
breweries <- read.csv("Dataset/Breweries.csv",stringsAsFactor=FALSE)

# Assign column names
colnames(beers) <- c("Beer","Beer_ID","ABV","IBU","Brewery_id","Style","Ounces")
colnames(breweries) <- c("Brew_ID","Breweries","City","State")
both <- beers %>% inner_join(breweries, by = c("Brewery_id" = "Brew_ID"))
```


## 1. How many breweries are present in each state?

``` {r Question_1}
brews_state <- breweries %>% group_by(State) %>% count()
brews_state

p.state <- ggplot(data=brews_state, aes(x=State, y=n, fill=State))
p.state <- p.state + geom_bar(stat="identity", color="black", position=position_dodge())+theme_minimal()
p.state <- p.state + geom_text(aes(label=n), vjust=1.6, position = position_dodge(0.9), size=2.5)
p.state

# Output brews_state data to csv for Excel charts for presentation
state.data <- "Beer_Case_Study_files/state.csv"
write.csv(brews_state, file = state.data)
```


## 2. Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file

```{r Question_2}
both <- beers %>% inner_join(breweries, by = c("Brewery_id" = "Brew_ID"))

both_full <- beers %>% full_join(breweries, by = c("Brewery_id" = "Brew_ID"))

head(both_full,6)
tail(both_full,6)
```


## 3. Report the number of NA's in each column.

```{r Question_3}
sapply(both, function(x) {sum(is.na(x))})
```


## 4. Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.

```{r Question_4}
ABV_IBU <- both %>% group_by(State) %>% summarise(ABV = median(ABV, na.rm = TRUE), IBU = median(IBU, na.rm = TRUE))

# Output ABV_IBU data by state to csv for Excel charts for presentation
ABV.IBU.data <- "Beer_Case_Study_files/ABV_IBU_by_State.csv"
write.csv(ABV_IBU, file = ABV.IBU.data)

p.ABV <- ggplot(data=ABV_IBU, aes(x=State, y=ABV, fill=State))
p.ABV <- p.ABV + geom_bar(stat="identity", color="black", position=position_dodge())+theme_minimal()
p.ABV <- p.ABV + geom_text(aes(label=ABV), vjust=1.6, position = position_dodge(0.9), size=2.5)
p.ABV


p.IBU <- ggplot(data=ABV_IBU, aes(x=State, y=IBU, fill=State))
p.IBU <- p.IBU + geom_bar(stat="identity", color="black", position=position_dodge())+theme_minimal()
p.IBU <- p.IBU + geom_text(aes(label=IBU), vjust=1.6, position = position_dodge(0.9), size=2.5)
p.IBU

```


## 5. Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?

```{r Question_5}
maxABV_IBU <- both %>% group_by(State) %>% summarise(ABV = max(ABV, na.rm = TRUE), IBU = max(IBU, na.rm = TRUE))
maxABV <- maxABV_IBU %>% filter(ABV == max(ABV))
maxIBU <- maxABV_IBU %>% filter(IBU == max(IBU))

maxABV[, c(1,2)]
maxIBU[, c(1,3)]
```

## 6. Summary statistics for the ABV variable

```{r Question_6}
summary(both$ABV)
```


## 7. Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot.

```{r Question_7}
lmABV_IBU <- na.omit(both)
p.ABV_IBU <- ggplot(lmABV_IBU, aes(x = ABV, y = IBU), na.rm = TRUE) + geom_point(na.rm = TRUE) + geom_rug() 
p.ABU_IBU <- p.ABV_IBU + geom_smooth(method=lm)
p.ABU_IBU

# Output ABV_IBU full data to csv for Excel charts for presentation
outputlink<- lmABV_IBU[,3:4]
linkData.data <- "Beer_Case_Study_files/ABV_IBU_link.csv"
write.csv(outputlink, file = linkData.data)
```


