---
title: "Beer Case Study"
author: "Satish, Tyler, Thotho"
date: "October 14, 2018"
output: github_document
---
**GitHub**:https://github.com/HammerLynch/MSDS6306_Case_Study_1

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### R-version info
Environment information where the code was executed.

```{r VersionData}
R.version
```


### Libraries and Initial Data Prepration
R Libraries required for the proejct  

* plyr
* dplyr
* tidyr
* ggplot2

Once the libraries are loaded, the data sets are loaded and prepared for further analysis.

```{r GatherData}
require(plyr)
require(dplyr)
require(tidyr)
require(ggplot2)

beers <- read.csv("Dataset/Beers.csv",stringsAsFactor=FALSE)
breweries <- read.csv("Dataset/Breweries.csv",stringsAsFactor=FALSE)

# Assign column names
colnames(beers) <- c("Beer","Beer_ID","ABV","IBU","Brewery_id","Style","Ounces")
colnames(breweries) <- c("Brew_ID","Breweries","City","State")
both <- beers %>% inner_join(breweries, by = c("Brewery_id" = "Brew_ID"))
```


### 1. How many breweries are present in each state?

Breweries across 50 states and 1 Federal District (DC) are shown below, where the state of Colorado has the highest number of breweries (47)

``` {r Question_1}
brews_state <- breweries %>% group_by(State) %>% count()
brews_state

#code for storing and output of ggplot - rainbow bars - black text
p.state <- ggplot(data=brews_state, aes(x=State, y=n, fill=State))
p.state <- p.state + geom_bar(stat="identity", color="black", position=position_dodge())+theme_minimal()
p.state <- p.state + geom_text(aes(label=n), vjust=1.6, position = position_dodge(0.9), size=2.5)
p.state

# Output brews_state data to csv for Excel charts for presentation
state.data <- "Beer_Case_Study_files/state.csv"
write.csv(brews_state, file = state.data)
```


### 2. Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file

Beers and Breweries data have been de-normalized into one set for further investigation into the data  


```{r Question_2}
both <- beers %>% inner_join(breweries, by = c("Brewery_id" = "Brew_ID"))

both_full <- beers %>% full_join(breweries, by = c("Brewery_id" = "Brew_ID"))

head(both_full,6)
tail(both_full,6)
```


### 3. Report the number of NA's in each column.

Missing information on the de-normalized data  

* 2.57% missing information about Alcohol by volume of the beer (ABV).
* 41.7% missing information on International Bitterness Units of the beer (IBU)


```{r Question_3}
sapply(both, function(x) {sum(is.na(x))})
```


### 4. Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.

* Median Alcohol by volume helps US Beer crafters to decide what should the concentration of the alcohol in the beers for their new factory.
* Median International Bitterness Units helps US Beer crafters to decide the bitterness taste choices by the users in the respective regions.    


```{r Question_4}
#consolidate ABV and IBU data into one
ABV_IBU <- both %>% group_by(State) %>% summarise(ABV = median(ABV, na.rm = TRUE), IBU = median(IBU, na.rm = TRUE))

# Output ABV_IBU data by state to csv for Excel charts for presentation
ABV.IBU.data <- "Beer_Case_Study_files/ABV_IBU_by_State.csv"
write.csv(ABV_IBU, file = ABV.IBU.data)

#code for storing and output of ggplot - rainbow bars - black text
p.ABV <- ggplot(data=ABV_IBU, aes(x=State, y=ABV, fill=State))
p.ABV <- p.ABV + geom_bar(stat="identity", color="black", position=position_dodge())+theme_minimal()
p.ABV <- p.ABV + geom_text(aes(label=ABV), vjust=1.6, position = position_dodge(0.9), size=2.5)
p.ABV

#code for storing and output of ggplot - rainbow bars - black text
p.IBU <- ggplot(data=ABV_IBU, aes(x=State, y=IBU, fill=State))
p.IBU <- p.IBU + geom_bar(stat="identity", color="black", position=position_dodge())+theme_minimal()
p.IBU <- p.IBU + geom_text(aes(label=IBU), vjust=1.6, position = position_dodge(0.9), size=2.5)
p.IBU

```


### 5. Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?

Oregon has been identified with the most bitter beers with IBU unit of 138 but the most Alcoholic beers have been crafted in CO with ABV units of 0.128

```{r Question_5}
#Determine max ABV and IBU
maxABV_IBU <- both %>% group_by(State) %>% summarise(ABV = max(ABV, na.rm = TRUE), IBU = max(IBU, na.rm = TRUE))
maxABV <- maxABV_IBU %>% filter(ABV == max(ABV))
maxIBU <- maxABV_IBU %>% filter(IBU == max(IBU))

maxABV[, c(1,2)]
maxIBU[, c(1,3)]
```

### 6. Summary statistics for the ABV variable

* ABV range is from .10% to 12.80%
* 50% of beers fall within the range of 3.78%-8.23%


```{r Question_6}
# Output summary of ABV
summary(both$ABV)
```


### 7. Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot.

* We could see that there is some linear relationship with between the IBU (bitterness value) and the ABV (Alcohol by volume) based on the scatter plot. An approximation was created with the a trendline:

* + 𝐼𝐵𝑈 ≈1282(𝐴𝐵𝑉)−34

* Exact inference can be drawn only after a causal study on the beers’ values.


```{r Question_7}
# Create data set with no NAs
lmABV_IBU <- na.omit(both)
p.ABV_IBU <- ggplot(lmABV_IBU, aes(x = ABV, y = IBU), na.rm = TRUE) + geom_point(na.rm = TRUE) + geom_rug() 
p.ABU_IBU <- p.ABV_IBU + geom_smooth(method=lm)
p.ABU_IBU

# Output ABV_IBU full data to csv for Excel charts for presentation
outputlink<- lmABV_IBU[,3:4]
linkData.data <- "Beer_Case_Study_files/ABV_IBU_link.csv"
write.csv(outputlink, file = linkData.data)
```


### Conclusion
* Based on the current data, it may be advantageous to open a new brewery in one of the locations shown on the map.  A darker color represents a state with a lower number of current breweries as well as less nearby competition.
* The target product should be in the higher ABV range of 7-10% due to current market saturation.


