---
title: "Codebook for beers"
date: "2018-10-13 17:34:56"
output:
  html_document:
    df_print: paged
subtitle: Team (Satish, Tyler, Thotho)
dataMaid: yes
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library("ggplot2")
library("pander")
```
```{r 'visualFunctions', echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
ggAggHist <- getFromNamespace("ggAggHist", "dataMaid")
ggAggBarplot <- getFromNamespace("ggAggBarplot", "dataMaid")
```
# Data report overview
The dataset examined has the following dimensions:


---------------------------------
Feature                    Result
------------------------ --------
Number of observations       2410

Number of variables             7
---------------------------------




# Codebook summary table

------------------------------------------------------------------------
Label   Variable            Class       # unique  Missing  Description  
                                          values                        
------- ------------------- --------- ---------- --------- -------------
        **[Name]**          factor          2305  0.00 %    Name of the beer            

        **[Beer\_ID]**      integer         2410  0.00 %    Unique identifier of the beer            

        **[ABV]**           numeric           75  2.57 %    Alcohol by volume of the beer.            

        **[IBU]**           integer          108  41.70 %   International Bitterness Units of the beer.            

        **[Brewery\_id]**   integer          558  0.00 %    Brewery id associated with the beer.            

        **[Style]**         factor           100  0.00 %    Style of the beer            

        **[Ounces]**        numeric            7  0.00 %    Ounces of beer            
------------------------------------------------------------------------




# Variable list
## Name

<div class = "row">
<div class = "col-lg-8">

---------------------------------------------------
Feature                                      Result
------------------------- -------------------------
Variable type                                factor

Number of missing obs.                      0 (0 %)

Number of unique values                        2305

Mode                              "Nonstop Hef Hop"

Reference category          #001 Golden Amber Lager
---------------------------------------------------


</div>

</div>




---

## Beer\_ID

<div class = "row">
<div class = "col-lg-8">

-------------------------------------------
Feature                              Result
------------------------- -----------------
Variable type                       integer

Number of missing obs.              0 (0 %)

Number of unique values                2410

Median                               1453.5

1st and 3rd quartiles       808.25; 2075.75

Min. and max.                       1; 2692
-------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-2-Beer-ID', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 200, 400, 600, 800, 
1000, 1200, 1400, 1600, 1800, 2000, 2200, 2400, 2600), xmax = c(200, 
400, 600, 800, 1000, 1200, 1400, 1600, 1800, 2000, 2200, 2400, 
2600, 2800), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0), ymax = c(162L, 87L, 165L, 181L, 172L, 194L, 194L, 190L, 198L, 
191L, 190L, 197L, 200L, 89L)), class = "data.frame", row.names = c(NA, 
-14L)), vnam = "Beer_ID")
```
</div>
</div>




---

## ABV

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.      62 (2.57 %)

Number of unique values              74

Median                             0.06

1st and 3rd quartiles        0.05; 0.07

Min. and max.                   0; 0.13
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-3-ABV', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.01, 0.02, 0.03, 
0.04, 0.05, 0.06, 0.07, 0.08, 0.09, 0.1, 0.11, 0.12), xmax = c(0.01, 
0.02, 0.03, 0.04, 0.05, 0.06, 0.07, 0.08, 0.09, 0.1, 0.11, 0.12, 
0.13), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 
0L, 3L, 73L, 599L, 780L, 483L, 216L, 109L, 80L, 1L, 1L, 2L)), class = "data.frame", row.names = c(NA, 
-13L)), vnam = "ABV")
```
</div>
</div>




---

## IBU

<div class = "row">
<div class = "col-lg-8">

-----------------------------------------
Feature                            Result
------------------------- ---------------
Variable type                     integer

Number of missing obs.      1005 (41.7 %)

Number of unique values               107

Median                                 35

1st and 3rd quartiles              21; 64

Min. and max.                      4; 138
-----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-4-IBU', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 10, 20, 30, 40, 50, 
60, 70, 80, 90, 100, 110, 120, 130), xmax = c(10, 20, 30, 40, 
50, 60, 70, 80, 90, 100, 110, 120, 130, 140), ymin = c(0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(58L, 280L, 275L, 
187L, 137L, 102L, 153L, 78L, 61L, 48L, 11L, 11L, 2L, 2L)), class = "data.frame", row.names = c(NA, 
-14L)), vnam = "IBU")
```
</div>
</div>




---

## Brewery\_id

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               integer

Number of missing obs.      0 (0 %)

Number of unique values         558

Median                          206

1st and 3rd quartiles       94; 367

Min. and max.                1; 558
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-5-Brewery-id', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 50, 100, 150, 200, 
250, 300, 350, 400, 450, 500, 550), xmax = c(50, 100, 150, 200, 
250, 300, 350, 400, 450, 500, 550, 600), ymin = c(0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(372L, 253L, 270L, 283L, 195L, 
180L, 176L, 247L, 155L, 136L, 129L, 14L)), class = "data.frame", row.names = c(NA, 
-12L)), vnam = "Brewery_id")
```
</div>
</div>




---

## Style

<div class = "row">
<div class = "col-lg-8">

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                       factor

Number of missing obs.             0 (0 %)

Number of unique values                100

Mode                        "American IPA"

Reference category                        
------------------------------------------


</div>

</div>

---

## Ounces

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           7

Median                           12

1st and 3rd quartiles        12; 16

Min. and max.               8.4; 32
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-7-Ounces', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(8L, 10L, 12L, 14L, 16L, 
18L, 20L, 22L, 24L, 26L, 28L, 30L), xmax = c(10L, 12L, 14L, 16L, 
18L, 20L, 22L, 24L, 26L, 28L, 30L, 32L), ymin = c(0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 1525L, 0L, 841L, 1L, 15L, 
0L, 22L, 0L, 0L, 0L, 5L)), class = "data.frame", row.names = c(NA, 
-12L)), vnam = "Ounces")
```
</div>
</div>




---


